Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2016-01-04 tmm.tex
Keep all expressions in the paper consistent
Remove the demo website

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
To cope with the challenge brought by bandwidth fluctuation and improve the experience of watching online videos, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC. First, a simple and effective linear error model is proposed and verified for quality scalability of SVC. The model exploits the linear feature of pixel value errors and can be used to accurately estimate the distortion caused by discarding any combination of enhancement data packets in an SVC bitstream. On that basis, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint. Finally, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment and determine the suitable bitrate for transmission. By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm is able to reduce quality fluctuation while still keeping a high quality level. Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with the PSNR average increased by 0.83 dB. The system is deployed at online video website www.7dlive.com and proves to be practically effective.
\end{abstract}

@@

To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction and the PID-based quality control algorithm. The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint. They work together to improve the user's experience of watching videos online. With DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.

In this section, we first present separate experiments to show the advantage of each proposed solution, then give the result when they are combined together. Readers who are interested in the practical implementation and demonstration can visit the online video website http://www.7dlive.com for more information.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
To cope with the challenge brought by bandwidth fluctuation and improve the experience of watching online videos, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC. First, a simple and effective linear error model is proposed and verified for quality scalability of SVC. The model exploits the linear feature of pixel value errors and can be used to accurately estimate the distortion caused by discarding any combination of enhancement data packets in an SVC bitstream. On that basis, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint. Finally, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment and determine the suitable bitrate for transmission. By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm is able to reduce quality fluctuation while still keeping a high quality level. Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with the PSNR average increased by 0.83 dB.
\end{abstract}

@@

To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction and the PID-based quality control algorithm. The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint. They work together to improve the user's experience of watching online videos. With DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.

In this section, we first present separate experiments to show the advantage of each proposed solution, then give the result when they are combined together.
